\documentclass[submission,copyright,creativecommons]{eptcs}
\providecommand{\event}{LFMTP 2018} % Name of the event you are submitting to
\usepackage{breakurl}             % Not needed if you use pdflatex only.
\usepackage{underscore}           % Only needed if you use pdflatex.

\pagenumbering{roman}

\begin{document}

\section*{Preface}

This volume contains a selection of papers presented at LFMTP 2018,
the 13th International Workshop on Logical Frameworks and
Meta-Languages: Theory and Practice (LFMTP), held on July 7, 2018, in
Oxford, UK. The workshop was affiliated with the 3rd International
Conference on Formal Structures for Computation and Deduction (FSCD)
within the 7th Federated Logic Conference (FLoC).

Logical frameworks and meta-languages form a common substrate for
representing, implementing and reasoning about a wide variety of
deductive systems of interest in logic and computer science. Their
design, implementation and their use in reasoning tasks, ranging from
the correctness of software to the properties of formal systems, have
been the focus of considerable research over the last two
decades. This workshop brought together designers, implementors and
practitioners to discuss various aspects impinging on the structure
and utility of logical frameworks, including the treatment of variable
binding, inductive and co-inductive reasoning techniques and the
expressiveness and lucidity of the reasoning process.

We received 13 submissions in total, which were reviewed by at least 3
program committee members or external reviewers. Out of those, 4 were
selected for presentation and 4 were selected for presentation and
publication. These proceedings include the latter 4 plus one invited
submission.

In addition to the submission presentations, the program included 3
invited talks by Delia Kesner (IRIF, CNRS and Universit\'{e} Paris
Diderot, France), Kuen-Bang Hou (Favonia) (Institute for Advanced
Study, Princeton, USA), and Grigore Rosu (University of Illinois at
Urbana-Champaign, USA).

Many people have contributed to the success of LFMTP'18. We would like
to thank the organization of FLoC for providing the infrastructure and
coordination with other events. We are grateful for the great program
committee who submitted all reviews on time and participated actively
on the decisions.  The authors and invited speakers are the ones
responsible for a very interesting program, and the attendees for
fruitful and stimulating discussions.
\medskip

\begin{flushright}
Fr\'{e}d\'{e}ric Blanqui \& Giselle Reis

May 31, 2018
\end{flushright}

\subsection*{Program Committee of LFMTP 2018}

\begin{itemize}\setlength\itemsep{0em}
  \item Mar\'{i}a Alpuente (Universitat Polit\`{e}cnica de Val\`{e}ncia, Spain)
  \item Andrej Bauer (University of Ljubljana, Slovenia)
  \item Fr\'{e}d\'{e}ric Blanqui (Inria, France), co-chair
  \item Ana Bove (Chalmers University of Technology, Sweden)
  \item St\'{e}phane Graham-Lengrand (CNRS, France)
  \item Makoto Hamana (Gunma University, Japan)
  \item Chantal Keller (Universit\'{e} Paris-Sud, France)
  \item Carlos Olarte (Universidade Federal do Rio Grande do Norte, Brazil)
  \item Giselle Reis (Carnegie Mellon University, Qatar), co-chair
  \item Aaron Stump (University of Iowa, USA)
  \item Yuting Wang (Yale University, USA)
\end{itemize}

\subsection*{Additional Reviewers}

  Arthur Charguéraud, Philipp Haselwarter, Matija Pretnar, and Nick Smallbone

\end{document}
